---
title: "aapi coalitions main analyses nov 2022"
author: "Stephanie Chan"
date: "11/3/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Read in data
```{r}

data<-read.csv("aapi coalitions data no zip nov 3 2022.csv",stringsAsFactors = F)

#get rid of extra rows at top
data<-data[3:nrow(data),]

#get rid of respondents who do not consent
d<-data[data$consent=="Yes, I give my consent.",]

#get rid of respondents who do not identify as at least partially Asian, deleted people who checked all races
d<-d[d$race=="Asian"|
     d$race=="White,Asian"|
     d$race=="Asian,Other"|
     d$race=="Asian,Middle Eastern"|
     d$race=="Hispanic or Latino,Asian"|
     d$race=="Black or African American,Asian"|
     d$race=="Asian,Native American" |
     d$race=="White,Asian,Other" |
     d$race=="White,Black or African American,Asian"|
     d$race=="White,Hispanic or Latino,Asian"|
     d$race=="Hispanic or Latino,Asian,Other"|
     d$race=="Black or African American,Hispanic or Latino,Asian"|
     d$race=="Black or African American,Asian,Native American",]

#keeping only those who passed the attention check
d<-d[d$attention1=="Extremely interested,Very interested",] 

```

##treatment variable
```{r}

#table(d$FL_6_DO) 

d$treat<-NA
d$treat[d$FL_6_DO=="treat1"]<-1
d$treat[d$FL_6_DO=="treat2"]<-2
d$treat[d$FL_6_DO=="treat3"]<-0

#recoding those who did not get a narrative but were still in another condition to be t3
d$treat[d$FL_6_DO=="BL_1z5uKt9r6f3OTCB"]<-0

table(d$treat)

```

##demographic factors
```{r}

##age
d$bornyear2<-as.numeric(d$bornyear)
d$bornyear2[d$bornyear2==-99]<-NA
d$age<-2022-d$bornyear2

##gender
d$fem<-NA
d$fem[d$gender=="man"]<-0
d$fem[d$gender=="woman"]<-1
d$fem[d$gender=="nonbinary"]<-0
d$fem[d$gender=="other"]<-0

##education
d$ed[d$education=="grade 1 to grade 8"]<-1
d$ed[d$education=="some high school"]<-2
d$ed[d$education=="high school graduate or GED"]<-3
d$ed[d$education=="some college or 2 year degree"]<-4
d$ed[d$education=="4 year college graduate"]<-5
d$ed[d$education=="post-graduate education"]<-6

d$ed<-as.numeric(d$ed)

##income
#coded so that less than $10,000 is 1
#$10,000-$19,999 is 2
#$20,000-$29,999 is 3
#$30,000-$39,999 is 4
#$40,000-$49,999 is 5
#$50,000-$59,999 is 6
#$60,000-$69,999 is 7
#$70,000-$79,999 is 8
#$80,000-$89,999 is 9
#$90,000-$99,999 is 10
#$100,000-$149,999 is 11
#$150,000-$199,999 is 12
#$200,000-$249,999 is 13
#over $250,000 is 14
d$inc<-NA
d$inc[d$income=="less than $10,000"]<-1
d$inc[d$income=="$10,000-$19,999"]<-2
d$inc[d$income=="$20,000-$29,999"]<-3
d$inc[d$income=="$30,000-$39,999"]<-4
d$inc[d$income=="$40,000-$49,999"]<-5
d$inc[d$income=="$50,000-$59,999"]<-6
d$inc[d$income=="$60,000-$69,999"]<-7
d$inc[d$income=="$70,000-$79,999"]<-8
d$inc[d$income=="$80,000-$89,999"]<-9
d$inc[d$income=="$90,000-$99,999"]<-10
d$inc[d$income=="$100,000-$149,999"]<-11
d$inc[d$income=="$150,000-$199,999"]<-12
d$inc[d$income=="$200,000-$249,999"]<-13
d$inc[d$income=="over $250,000"]<-14

##immigration generation
d$immgen<-NA
d$immgen[d$immstat=="My parents, grandparents, and I were all born in the United States."]<-4
d$immgen[d$immstat=="My parents and I were born in the United States but at least one of my grandparents was an immigrant."]<-3
d$immgen[d$immstat=="I was born outside the United States and am not a U.S. citizen."]<-1
d$immgen[d$immstat=="I was born in the United States and both of my parents are immigrants."]<-2
d$immgen[d$immstat=="I was born in the United States and one of my parents is an immigrant."]<-2
d$immgen[d$immstat=="I was born outside the United States and am a U.S. citizen."]<-1

#noncitizen
#1 if a non-citizen, 0 otherwise
d$noncit<-NA
d$noncit[d$immstat=="My parents, grandparents, and I were all born in the United States."]<-0
d$noncit[d$immstat=="My parents and I were born in the United States but at least one of my grandparents was an immigrant."]<-0
d$noncit[d$immstat=="I was born outside the United States and am not a U.S. citizen."]<-1
d$noncit[d$immstat=="I was born in the United States and both of my parents are immigrants."]<-0
d$noncit[d$immstat=="I was born in the United States and one of my parents is an immigrant."]<-0
d$noncit[d$immstat=="I was born outside the United States and am a U.S. citizen."]<-0

#partisanship (democrats are lower numbers, republicans are higher numbers)
d$partisan<-NA
d$partisan[d$partisan2=="Strong Republican"]<-7
d$partisan[d$partisan2=="Not very strong Republican"]<-6
d$partisan[d$partisan4=="Republican"]<-5
d$partisan[d$partisan4=="No preference"]<-4
d$partisan[d$partisan4=="Democratic"]<-3
d$partisan[d$partisan3=="Not very strong Democrat"]<-2
d$partisan[d$partisan3=="Strong Democrat"]<-1

```

##network measures
```{r}

#number of named alters
d$netgen1<-NA
d$netgen2<-NA
d$netgen3<-NA
d$netgen4<-NA
d$netgen5<-NA

for(a in 1:nrow(d)){
  for(b in 56:60){
    d[a,b+85]<-ifelse(d[a,b]!="",1,0)
  }
}

d$netgen1[is.na(d$netgen1)]<-0
d$netgen2[is.na(d$netgen2)]<-0
d$netgen3[is.na(d$netgen3)]<-0
d$netgen4[is.na(d$netgen4)]<-0
d$netgen5[is.na(d$netgen5)]<-0

d$netnum<-NA

for(i in 1:nrow(d)){
  d$netnum[i]<-sum(d[i,141:145])
}

#network care about participating in politics
#disapprove is -1
#would not care is 0
#would approve is 1
d$netpart1<-NA
d$netpart1[d$X1_netpart=="They would disapprove."]<--1
d$netpart1[d$X1_netpart=="They would not care."]<-0
d$netpart1[d$X1_netpart=="They would approve."]<-1

d$netpart2<-NA
d$netpart2[d$X2_netpart=="They would disapprove."]<--1
d$netpart2[d$X2_netpart=="They would not care."]<-0
d$netpart2[d$X2_netpart=="They would approve."]<-1

d$netpart3<-NA
d$netpart3[d$X3_netpart=="They would disapprove."]<--1
d$netpart3[d$X3_netpart=="They would not care."]<-0
d$netpart3[d$X3_netpart=="They would approve."]<-1

d$netpart4<-NA
d$netpart4[d$X4_netpart=="They would disapprove."]<--1
d$netpart4[d$X4_netpart=="They would not care."]<-0
d$netpart4[d$X4_netpart=="They would approve."]<-1

d$netpart5<-NA
d$netpart5[d$X5_netpart=="They would disapprove."]<--1
d$netpart5[d$X5_netpart=="They would not care."]<-0
d$netpart5[d$X5_netpart=="They would approve."]<-1

d$netpart<-NA
for(i in 1:nrow(d)){
  d[i,152]<-sum(d[i,147:151],na.rm=TRUE) 
}

#network care about support for blm
#disapprove is -1
#would not care is 0
#would approve is 1
d$netblm1<-NA
d$netblm1[d$X1_netsupp1=="They would disapprove."]<--1
d$netblm1[d$X1_netsupp1=="They would not care."]<-0
d$netblm1[d$X1_netsupp1=="They would approve."]<-1

d$netblm2<-NA
d$netblm2[d$X2_netsupp1=="They would disapprove."]<--1
d$netblm2[d$X2_netsupp1=="They would not care."]<-0
d$netblm2[d$X2_netsupp1=="They would approve."]<-1

d$netblm3<-NA
d$netblm3[d$X3_netsupp1=="They would disapprove."]<--1
d$netblm3[d$X3_netsupp1=="They would not care."]<-0
d$netblm3[d$X3_netsupp1=="They would approve."]<-1

d$netblm4<-NA
d$netblm4[d$X4_netsupp1=="They would disapprove."]<--1
d$netblm4[d$X4_netsupp1=="They would not care."]<-0
d$netblm4[d$X4_netsupp1=="They would approve."]<-1

d$netblm5<-NA
d$netblm5[d$X5_netsupp1=="They would disapprove."]<--1
d$netblm5[d$X5_netsupp1=="They would not care."]<-0
d$netblm5[d$X5_netsupp1=="They would approve."]<-1

d$netblm<-NA
for(i in 1:nrow(d)){
  d[i,158]<-sum(d[i,153:157],na.rm=TRUE) 
}

#network care about support for Stop Asian Hate
#disapprove is -1
#would not care is 0
#would approve is 1
d$netstop1<-NA
d$netstop1[d$X1_netsupp2=="They would disapprove."]<--1
d$netstop1[d$X1_netsupp2=="They would not care."]<-0
d$netstop1[d$X1_netsupp2=="They would approve."]<-1

d$netstop2<-NA
d$netstop2[d$X2_netsupp2=="They would disapprove."]<--1
d$netstop2[d$X2_netsupp2=="They would not care."]<-0
d$netstop2[d$X2_netsupp2=="They would approve."]<-1

d$netstop3<-NA
d$netstop3[d$X3_netsupp2=="They would disapprove."]<--1
d$netstop3[d$X3_netsupp2=="They would not care."]<-0
d$netstop3[d$X3_netsupp2=="They would approve."]<-1

d$netstop4<-NA
d$netstop4[d$X4_netsupp2=="They would disapprove."]<--1
d$netstop4[d$X4_netsupp2=="They would not care."]<-0
d$netstop4[d$X4_netsupp2=="They would approve."]<-1

d$netstop5<-NA
d$netstop5[d$X5_netsupp2=="They would disapprove."]<--1
d$netstop5[d$X5_netsupp2=="They would not care."]<-0
d$netstop5[d$X5_netsupp2=="They would approve."]<-1

d$netstop<-NA
for(i in 1:nrow(d)){
  d[i,164]<-sum(d[i,159:163],na.rm=TRUE) 
}

```

##outcomes
political participation
```{r}

#intend_1-attend local meeting
d$intend1[d$intend_1=="-99"]<-NA
d$intend1[d$intend_1=="Yes"]<-1
d$intend1[d$intend_1=="No"]<-0

#intend_2-put up political sign
d$intend2[d$intend_2=="-99"]<-NA
d$intend2[d$intend_2=="Yes"]<-1
d$intend2[d$intend_2=="No"]<-0

#intend_3-work for campaign or candidate
d$intend3[d$intend_3=="-99"]<-NA
d$intend3[d$intend_3=="Yes"]<-1
d$intend3[d$intend_3=="No"]<-0

#intend_4-protest
d$intend4[d$intend_4=="-99"]<-NA
d$intend4[d$intend_4=="Yes"]<-1
d$intend4[d$intend_4=="No"]<-0

#intend_5-contact public official
d$intend5[d$intend_5=="-99"]<-NA
d$intend5[d$intend_5=="Yes"]<-1
d$intend5[d$intend_5=="No"]<-0

#intend_6-donate money
d$intend6[d$intend_6=="-99"]<-NA
d$intend6[d$intend_6=="Yes"]<-1
d$intend6[d$intend_6=="No"]<-0

#intend_7-vote
d$intend7[d$intend_7=="-99"]<-NA
d$intend7[d$intend_7=="Yes"]<-1
d$intend7[d$intend_7=="No"]<-0

#intend_8-discuss politics
d$intend8[d$intend_8=="-99"]<-NA
d$intend8[d$intend_8=="Yes"]<-1
d$intend8[d$intend_8=="No"]<-0

```

polmove
How much do you support or oppose the following policies, social movements, or organizations?
1 indicates strongly support, 0 indicates strongly oppose
```{r}

#polmove_1 affirmative action
d$pmove1<-NA
d$pmove1[d$polmove_1=="Strongly oppose"]<-0
d$pmove1[d$polmove_1=="Oppose"]<-1/4
d$pmove1[d$polmove_1=="Neither support or oppose"]<-2/4
d$pmove1[d$polmove_1=="Support"]<-3/4
d$pmove1[d$polmove_1=="Strongly support"]<-4/4

#polmove_2 pathway to citizenship
d$pmove2<-NA
d$pmove2[d$polmove_2=="Strongly oppose"]<-0
d$pmove2[d$polmove_2=="Oppose"]<-1/4
d$pmove2[d$polmove_2=="Neither support or oppose"]<-2/4
d$pmove2[d$polmove_2=="Support"]<-3/4
d$pmove2[d$polmove_2=="Strongly support"]<-4/4

#polmove_3 government provided healthcare
d$pmove3<-NA
d$pmove3[d$polmove_3=="Strongly oppose"]<-0
d$pmove3[d$polmove_3=="Oppose"]<-1/4
d$pmove3[d$polmove_3=="Neither support or oppose"]<-2/4
d$pmove3[d$polmove_3=="Support"]<-3/4
d$pmove3[d$polmove_3=="Strongly support"]<-4/4

#polmove_4 social security
d$pmove4<-NA
d$pmove4[d$polmove_4=="Strongly oppose"]<-0
d$pmove4[d$polmove_4=="Oppose"]<-1/4
d$pmove4[d$polmove_4=="Neither support or oppose"]<-2/4
d$pmove4[d$polmove_4=="Support"]<-3/4
d$pmove4[d$polmove_4=="Strongly support"]<-4/4

#polmove_5 blm
d$pmove5<-NA
d$pmove5[d$polmove_5=="Strongly oppose"]<-0
d$pmove5[d$polmove_5=="Oppose"]<-1/4
d$pmove5[d$polmove_5=="Neither support or oppose"]<-2/4
d$pmove5[d$polmove_5=="Support"]<-3/4
d$pmove5[d$polmove_5=="Strongly support"]<-4/4

#polmove_6 reparations for descendants of enslaved persons
d$pmove6<-NA
d$pmove6[d$polmove_6=="Strongly oppose"]<-0
d$pmove6[d$polmove_6=="Oppose"]<-1/4
d$pmove6[d$polmove_6=="Neither support or oppose"]<-2/4
d$pmove6[d$polmove_6=="Support"]<-3/4
d$pmove6[d$polmove_6=="Strongly support"]<-4/4

#polmove_7 stop asian hate
d$pmove7<-NA
d$pmove7[d$polmove_7=="Strongly oppose"]<-0
d$pmove7[d$polmove_7=="Oppose"]<-1/4
d$pmove7[d$polmove_7=="Neither support or oppose"]<-2/4
d$pmove7[d$polmove_7=="Support"]<-3/4
d$pmove7[d$polmove_7=="Strongly support"]<-4/4

#polmove_8 nra
d$pmove8<-NA
d$pmove8[d$polmove_8=="Strongly oppose"]<-0
d$pmove8[d$polmove_8=="Oppose"]<-1/4
d$pmove8[d$polmove_8=="Neither support or oppose"]<-2/4
d$pmove8[d$polmove_8=="Support"]<-3/4
d$pmove8[d$polmove_8=="Strongly support"]<-4/4

#polmove_9 no exceptions abortion ban
d$pmove9<-NA
d$pmove9[d$polmove_9=="Strongly oppose"]<-0
d$pmove9[d$polmove_9=="Oppose"]<-1/4
d$pmove9[d$polmove_9=="Neither support or oppose"]<-2/4
d$pmove9[d$polmove_9=="Support"]<-3/4
d$pmove9[d$polmove_9=="Strongly support"]<-4/4

```

get info
```{r}

#getinfo_1 (multiracial coalition to fight discrimination)
d$info1[d$getinfo_1=="Yes"]<-1
d$info1[d$getinfo_1=="No"]<-0
d$info1[d$getinfo_1==""]<-NA

#getinfo_2 (asian americans against discrimination)
d$info2[d$getinfo_2=="Yes"]<-1
d$info2[d$getinfo_2=="No"]<-0
d$info2[d$getinfo_2==""]<-NA

#getinfo_3 (asian americans against affirmative action)
d$info3[d$getinfo_3=="Yes"]<-1
d$info3[d$getinfo_3=="No"]<-0
d$info3[d$getinfo_3==""]<-NA

#getinfo_4 (blm)
d$info4[d$getinfo_4=="Yes"]<-1
d$info4[d$getinfo_4=="No"]<-0
d$info4[d$getinfo_4==""]<-NA

#getinfo_5 (cair campaign to end muslim ban)
d$info5[d$getinfo_5=="Yes"]<-1
d$info5[d$getinfo_5=="No"]<-0
d$info5[d$getinfo_5==""]<-NA

```

idmag
How much do you identify as or with
```{r}

#idmag_1 person of color
d$idmag1<-NA
d$idmag1[d$idmag_1=="None at all"]<-0
d$idmag1[d$idmag_1=="A little"]<-1/3
d$idmag1[d$idmag_1=="Some"]<-2/3
d$idmag1[d$idmag_1=="A lot"]<-3/3

#idmag_2 immigrant
d$idmag2<-NA
d$idmag2[d$idmag_2=="None at all"]<-0
d$idmag2[d$idmag_2=="A little"]<-1/3
d$idmag2[d$idmag_2=="Some"]<-2/3
d$idmag2[d$idmag_2=="A lot"]<-3/3

#idmag_3 self-identified gender
d$idmag3<-NA
d$idmag3[d$idmag_3=="None at all"]<-0
d$idmag3[d$idmag_3=="A little"]<-1/3
d$idmag3[d$idmag_3=="Some"]<-2/3
d$idmag3[d$idmag_3=="A lot"]<-3/3

#idmag_4 asian american
d$idmag4<-NA
d$idmag4[d$idmag_4=="None at all"]<-0
d$idmag4[d$idmag_4=="A little"]<-1/3
d$idmag4[d$idmag_4=="Some"]<-2/3
d$idmag4[d$idmag_4=="A lot"]<-3/3

#idmag_5 national origin
d$idmag5<-NA
d$idmag5[d$idmag_5=="None at all"]<-0
d$idmag5[d$idmag_5=="A little"]<-1/3
d$idmag5[d$idmag_5=="Some"]<-2/3
d$idmag5[d$idmag_5=="A lot"]<-3/3

```


linked fate
What generally happens to the following groups in this country will have something to do with what happens in my life:
```{r}

#white
d$link1<-NA
d$link1[d$linkfate_1=="None at all"]<-0/3
d$link1[d$linkfate_1=="A little"]<-1/3
d$link1[d$linkfate_1=="Some"]<-2/3
d$link1[d$linkfate_1=="A lot"]<-3/3

#Black people
d$link2<-NA
d$link2[d$linkfate_2=="None at all"]<-0/3
d$link2[d$linkfate_2=="A little"]<-1/3
d$link2[d$linkfate_2=="Some"]<-2/3
d$link2[d$linkfate_2=="A lot"]<-3/3

#Asian Americans
d$link3<-NA
d$link3[d$linkfate_3=="None at all"]<-0/3
d$link3[d$linkfate_3=="A little"]<-1/3
d$link3[d$linkfate_3=="Some"]<-2/3
d$link3[d$linkfate_3=="A lot"]<-3/3

#Latinos
d$link4<-NA
d$link4[d$linkfate_4=="None at all"]<-0/3
d$link4[d$linkfate_4=="A little"]<-1/3
d$link4[d$linkfate_4=="Some"]<-2/3
d$link4[d$linkfate_4=="A lot"]<-3/3

```

linked fate discrimination
How much do you think discrimination against Asian Americans is connected to discrimination against:
```{r}

#white
d$linkdis1<-NA
d$linkdis1[d$linkfatedis_1=="None at all"]<-0/3
d$linkdis1[d$linkfatedis_1=="A little"]<-1/3
d$linkdis1[d$linkfatedis_1=="Some"]<-2/3
d$linkdis1[d$linkfatedis_1=="A lot"]<-3/3

#Black people
d$linkdis2<-NA
d$linkdis2[d$linkfatedis_2=="None at all"]<-0/3
d$linkdis2[d$linkfatedis_2=="A little"]<-1/3
d$linkdis2[d$linkfatedis_2=="Some"]<-2/3
d$linkdis2[d$linkfatedis_2=="A lot"]<-3/3

#Women
d$linkdis3<-NA
d$linkdis3[d$linkfatedis_3=="None at all"]<-0/3
d$linkdis3[d$linkfatedis_3=="A little"]<-1/3
d$linkdis3[d$linkfatedis_3=="Some"]<-2/3
d$linkdis3[d$linkfatedis_3=="A lot"]<-3/3

#Latinos
d$linkdis4<-NA
d$linkdis4[d$linkfatedis_4=="None at all"]<-0/3
d$linkdis4[d$linkfatedis_4=="A little"]<-1/3
d$linkdis4[d$linkfatedis_4=="Some"]<-2/3
d$linkdis4[d$linkfatedis_4=="A lot"]<-3/3

#Muslim Americans
d$linkdis5<-NA
d$linkdis5[d$linkfatedis_5=="None at all"]<-0/3
d$linkdis5[d$linkfatedis_5=="A little"]<-1/3
d$linkdis5[d$linkfatedis_5=="Some"]<-2/3
d$linkdis5[d$linkfatedis_5=="A lot"]<-3/3

```

closeness
coded so that 0 is "Not close at all" and 1 is "Very close"
How close do you feel your ideas, interests, and feelings are to people who are:
```{r}

#white people
d$close1<-NA
d$close1[d$closeness_1=="Not close at all"]<-0/3
d$close1[d$closeness_1=="Not too close"]<-1/3
d$close1[d$closeness_1=="Fairly close"]<-2/3
d$close1[d$closeness_1=="Very close"]<-3/3

#black people
d$close2<-NA
d$close2[d$closeness_2=="Not close at all"]<-0/3
d$close2[d$closeness_2=="Not too close"]<-1/3
d$close2[d$closeness_2=="Fairly close"]<-2/3
d$close2[d$closeness_2=="Very close"]<-3/3

#asian americans
d$close3<-NA
d$close3[d$closeness_3=="Not close at all"]<-0/3
d$close3[d$closeness_3=="Not too close"]<-1/3
d$close3[d$closeness_3=="Fairly close"]<-2/3
d$close3[d$closeness_3=="Very close"]<-3/3

#latinos
d$close4<-NA
d$close4[d$closeness_4=="Not close at all"]<-0/3
d$close4[d$closeness_4=="Not too close"]<-1/3
d$close4[d$closeness_4=="Fairly close"]<-2/3
d$close4[d$closeness_4=="Very close"]<-3/3

```

discrimination
coded such that 0 is "none at all" and 1 is "a great deal"
```{r}
#discrimination towards white people
d$dis1<-NA
d$dis1[d$discrimination_1=="None at all"]<-0/4
d$dis1[d$discrimination_1=="A little"]<-1/4
d$dis1[d$discrimination_1=="A moderate amount"]<-2/4
d$dis1[d$discrimination_1=="A lot"]<-3/4
d$dis1[d$discrimination_1=="A great deal"]<-4/4

#discrimination towards black people
d$dis2<-NA
d$dis2[d$discrimination_2=="None at all"]<-0/4
d$dis2[d$discrimination_2=="A little"]<-1/4
d$dis2[d$discrimination_2=="A moderate amount"]<-2/4
d$dis2[d$discrimination_2=="A lot"]<-3/4
d$dis2[d$discrimination_2=="A great deal"]<-4/4

#discrimination towards asian americans
d$dis3<-NA
d$dis3[d$discrimination_3=="None at all"]<-0/4
d$dis3[d$discrimination_3=="A little"]<-1/4
d$dis3[d$discrimination_3=="A moderate amount"]<-2/4
d$dis3[d$discrimination_3=="A lot"]<-3/4
d$dis3[d$discrimination_3=="A great deal"]<-4/4

#discrimination towards immigrants
d$dis4<-NA
d$dis4[d$discrimination_4=="None at all"]<-0/4
d$dis4[d$discrimination_4=="A little"]<-1/4
d$dis4[d$discrimination_4=="A moderate amount"]<-2/4
d$dis4[d$discrimination_4=="A lot"]<-3/4
d$dis4[d$discrimination_4=="A great deal"]<-4/4

#discrimination towards latinos
d$dis5<-NA
d$dis5[d$discrimination_5=="None at all"]<-0/4
d$dis5[d$discrimination_5=="A little"]<-1/4
d$dis5[d$discrimination_5=="A moderate amount"]<-2/4
d$dis5[d$discrimination_5=="A lot"]<-3/4
d$dis5[d$discrimination_5=="A great deal"]<-4/4

#discrimination towards lgbtq
d$dis6<-NA
d$dis6[d$discrimination_6=="None at all"]<-0/4
d$dis6[d$discrimination_6=="A little"]<-1/4
d$dis6[d$discrimination_6=="A moderate amount"]<-2/4
d$dis6[d$discrimination_6=="A lot"]<-3/4
d$dis6[d$discrimination_6=="A great deal"]<-4/4

#discrimination towards muslims
d$dis7<-NA
d$dis7[d$discrimination_7=="None at all"]<-0/4
d$dis7[d$discrimination_7=="A little"]<-1/4
d$dis7[d$discrimination_7=="A moderate amount"]<-2/4
d$dis7[d$discrimination_7=="A lot"]<-3/4
d$dis7[d$discrimination_7=="A great deal"]<-4/4

#discrimination towards women
d$dis8<-NA
d$dis8[d$discrimination_8=="None at all"]<-0/4
d$dis8[d$discrimination_8=="A little"]<-1/4
d$dis8[d$discrimination_8=="A moderate amount"]<-2/4
d$dis8[d$discrimination_8=="A lot"]<-3/4
d$dis8[d$discrimination_8=="A great deal"]<-4/4

```

resentment
racial resentment measures, coded -1 to 1
recoded such that -1 is least progressive and 1 is most progressive
0 is neither agree nor disagre

```{r}

#resentment1: I am angry that racism exists
d$resent1<-NA
d$resent1[d$resentment_1=="Strongly Disagree"]<--3/3
d$resent1[d$resentment_1=="Disagree"]<--2/3
d$resent1[d$resentment_1=="Somewhat disagree"]<--1/3
d$resent1[d$resentment_1=="Neither agree nor disagree"]<-0/3
d$resent1[d$resentment_1=="Somewhat agree"]<-1/3
d$resent1[d$resentment_1=="Agree"]<-2/3
d$resent1[d$resentment_1=="Strongly agree"]<-3/3

#resentment 2: White people in the United States have certain advantages because of the color of their skin.
d$resent2<-NA
d$resent2[d$resentment_2=="Strongly Disagree"]<--3/3
d$resent2[d$resentment_2=="Disagree"]<--2/3
d$resent2[d$resentment_2=="Somewhat disagree"]<--1/3
d$resent2[d$resentment_2=="Neither agree nor disagree"]<-0/3
d$resent2[d$resentment_2=="Somewhat agree"]<-1/3
d$resent2[d$resentment_2=="Agree"]<-2/3
d$resent2[d$resentment_2=="Strongly agree"]<-3/3

#resentment 3: I often find myself fearful of people of other races.-reverse coded
d$resent3<-NA
d$resent3[d$resentment_3=="Strongly Disagree"]<-3/3
d$resent3[d$resentment_3=="Disagree"]<-2/3
d$resent3[d$resentment_3=="Somewhat disagree"]<-1/3
d$resent3[d$resentment_3=="Neither agree nor disagree"]<-0/3
d$resent3[d$resentment_3=="Somewhat agree"]<--1/3
d$resent3[d$resentment_3=="Agree"]<--2/3
d$resent3[d$resentment_3=="Strongly agree"]<--3/3

#resentment 4: Racial problems in the United States are rare, isolated situations.-reverse coded
d$resent4<-NA
d$resent4[d$resentment_4=="Strongly Disagree"]<-3/3
d$resent4[d$resentment_4=="Disagree"]<-2/3
d$resent4[d$resentment_4=="Somewhat disagree"]<-1/3
d$resent4[d$resentment_4=="Neither agree nor disagree"]<-0/3
d$resent4[d$resentment_4=="Somewhat agree"]<--1/3
d$resent4[d$resentment_4=="Agree"]<--2/3
d$resent4[d$resentment_4=="Strongly agree"]<--3/3

```

manipulation checks
manipulation 1
How much do you agree with the following statements? - Asian Americans face similar levels of discrimination to other racial minority groups in the COVID-19 era.
```{r}

d$mani1<-NA
d$mani1[d$manipulation_1=="Disagree strongly"]<-0
d$mani1[d$manipulation_1=="Disagree somewhat"]<-1/4
d$mani1[d$manipulation_1=="Neither agree nor disagree"]<-2/4
d$mani1[d$manipulation_1=="Agree somewhat"]<-3/4
d$mani1[d$manipulation_1=="Agree strongly"]<-4/4

```

manipulation 2
How much do you agree with the following statements? - Asian Americans face discrimination in the COVID-19 era.
```{r}

d$mani2<-NA
d$mani2[d$manipulation_2=="Disagree strongly"]<-0
d$mani2[d$manipulation_2=="Disagree somewhat"]<-1/4
d$mani2[d$manipulation_2=="Neither agree nor disagree"]<-2/4
d$mani2[d$manipulation_2=="Agree somewhat"]<-3/4
d$mani2[d$manipulation_2=="Agree strongly"]<-4/4

```

balance test
none of the differences are statiscally significant (nothing p<0.1)
```{r}

#gender
t.test(d$fem[d$treat==1],d$fem[d$treat==0])
t.test(d$fem[d$treat==2],d$fem[d$treat==0])

#education
t.test(d$ed[d$treat==1],d$ed[d$treat==0])
t.test(d$ed[d$treat==2],d$ed[d$treat==0])

#partisanship
t.test(d$partisan[d$treat==1],d$partisan[d$treat==0])
t.test(d$partisan[d$treat==2],d$partisan[d$treat==0])

#age
t.test(d$age[d$treat==1],d$age[d$treat==0])
t.test(d$age[d$treat==2],d$age[d$treat==0])

#income
t.test(d$inc[d$treat==1],d$inc[d$treat==0])
t.test(d$inc[d$treat==2],d$inc[d$treat==0])

#immigrant generation
t.test(d$immgen[d$treat==1],d$immgen[d$treat==0])
t.test(d$immgen[d$treat==2],d$immgen[d$treat==0])

#noncitizen
t.test(d$noncit[d$treat==1],d$noncit[d$treat==0])
t.test(d$noncit[d$treat==2],d$noncit[d$treat==0])

```

write out recoded data
```{r}

#write.csv(d,"aapi coalitions data recoded nov 3 2022.csv")

```


checking correlation between liberal/conservative and dem/rep
```{r}


d$myideo<-d$ideo
d$myideo<-NA
d$myideo[d$ideo=="Very conservative" ]<-7
d$myideo[d$ideo=="Conservative"]<-6
d$myideo[d$ideo=="Somewhat conservative"]<-5
d$myideo[d$ideo=="Moderate or middle of the road"]<-4
d$myideo[d$ideo=="Somewhat liberal"]<-3
d$myideo[d$ideo=="Liberal"]<-2
d$myideo[d$ideo=="Very liberal"]<-1  
#d$myideo[d$ideo=="Not sure"]<-   

cor(d$myideo,d$partisan,use="complete.obs")

cor(d$myideo[d$immgen==1],d$partisan[d$immgen==1],use="complete.obs")

nrow(d[d$myideo=="Not sure",])

nrow(d[d$myideo=="Not sure" & d$immgen==1,])/nrow(d[d$immgen==1,])
nrow(d[d$myideo=="Not sure" & d$immgen==2,])/nrow(d[d$immgen==2,])
nrow(d[d$myideo=="Not sure" & d$immgen==3,])/nrow(d[d$immgen==3,])

```

checking scaling racial resentment scale
```{r}
library(ltm)

trial<-data.frame(cbind(d$resent1,d$resent2,d$resent3,d$resent4))

alpha<-cronbach.alpha(trial,na.rm=TRUE,standardized=TRUE) #cronbach's alpha was: 0.357, standardized as 0.377


```















































